A holomorphic approach to membranes and fivebranes

### 2022-06-07 fivebranes/fact.tex
merge

\documentclass[11pt]{amsart}

%\usepackage{../macros-master}
\usepackage{macros-fivebrane}

\begin{document}

@@

\begin{dfn}
Let $\cL$ be a local $L_\infty$ algebra on a manifold $M$ and consider the factorization algebra $\clie^\bu(\cL)$ which assigns to an open set $U \subset M$ the cochain complex $\clie^\bu(\cL(U))$. 
The \defterm{Koszul dual factorization algebra} is 
\[
\clie^\bu(\cL(U))^! \define \clie_\bu (\cL_{c}(U)) .
\]
In other words, the Koszul dual factorization algebra of $\clie^\bu(\cL)$ is the (untwisted) factorization enveloping algebra of the local Lie algebra $\cL$. 
\end{dfn}

@@

For any open set $U \subset \C^3$ we can consider the following $\C^\times$ action on the fields of the eleven-dimensional theory supported on $\R \times \C^2 \times U$ defined by
\begin{itemize}
\item On the fields $\mu(t;w,z) \in \Omega^\bu(\R) \otimes \PV^{1,\bu}(\C^2 \times U)$ the action is
\[
\lambda \cdot \mu(t;w,z) = \mu(\lambda t;\lambda w , z).
\]
\item On the fields $\nu(t;w,z) \in \Omega^\bu(\R) \otimes \PV^{0,\bu}(\C^2 \times U)$ the action is
\[
\lambda \cdot \nu(t;w,z) = \nu(\lambda t;\lambda w , z).
\]
\item On the fields $\beta(t;w,z) \in \Omega^\bu(\R) \otimes \Omega^{0,\bu}(\C^2 \times U)$ the action is
\[
\lambda \cdot \beta(t;w,z) = \lambda^{-1} \beta(\lambda t;\lambda w , z).
\]
\item On the fields $\mu(t;w,z) \in \Omega^\bu(\R) \otimes \Omega^{1,\bu}(\C^2 \times U)$ the action is
\[
\lambda \cdot \gamma(t;w,z) = \lambda^{-1} \gamma(\lambda t;\lambda w , z).
\]
\end{itemize}

@@

\begin{prop}
For each $n$, the sheaf of cochain complexes $U \mapsto \pi_* \cL_{sugra}(U)^{(n)}$ is quasi-isomorphic to one of the form
\[
\Omega^{0,\bu}(U, \cV^{(n)})
\]
for some finite rank super holomorphic vector bundle $\cV^{(n)}$ on $\C^3$. 
In particular, this endows $\Bar{\pi}_* \cL_{sugra}$ with the structure of a pro-vector bundle on $\C^3$. 
\end{prop}

@@

\begin{prop}
Let $Z$ be a Calabi--Yau three-fold and $\pi \colon Z \times \C^2 \times \R \to Z$ be the projection. 
There is a pro local Lie algebra $\cL_{\pi, sugra}$ on $Z$ such that:
\begin{itemize}
\item[(1)] there is a natural inclusion of of factorization algebras on $Z$
\[
\Bar{\pi}_* \Obs_{sugra} \hookrightarrow \pi_* \Obs_{sugra}
\]
which is dense at the level of cohomology. 
\item[(2)] there is a weight grading on $\cL_{\pi,sugra}$ which is concentrated in degrees $\geq -1$ and gives rise to a decomposition of vector bundles
\beqn\label{eqn:decomp3}
\Bar{\pi}_{*} \cL_{sugra} = \prod_{n \geq -1} \cV_{n} 
\eeqn
\item[(3)]
In weight zero, there is an equivalence of local Lie algebras on $Z$ 
\[
\cV_0 \simeq \cE(3|6)|Z .
\]
\end{itemize}
\end{prop}

@@

@@

\begin{prop}
On flat space 
\end{prop}

\end{document}

>>>>

%\documentclass[11pt]{amsart}

%\usepackage{../macros-master}
%\usepackage{macros-fivebrane}

%\begin{document}

@@

In analogy with the case of $\EE_1$, or locally constant factorization, algebras above we make the following definition.

\begin{dfn}
Let $\cL$ be a local $L_\infty$ algebra on a manifold $M$ and consider the factorization algebra $\clie^\bu(\cL)$ which assigns to an open set $U \subset M$ the cochain complex $\clie^\bu(\cL(U))$. 
The \defterm{$!$-dual factorization algebra} is 
\[
\clie^\bu(\cL)^! \define \clie_\bu (\cL_{c}) 
\]
where $\clie_\bu(\cL_c)$ assigns to an open set $U \subset M$ the cochain complex $\clie_\bu(\cL_c(U))$.
In other words, the $!$-dual factorization algebra of $\clie^\bu(\cL)$ is the (untwisted) factorization enveloping algebra of the local Lie algebra $\cL$. 
\end{dfn}

There are many things lacking in this definition. 
First off we do not define the $!$-dual for an arbitrary factorization algebra, only for ones of the form $\clie^\bu(\cL)$ where $\cL$ is a local Lie algebra. 
Also, we will not prove that $!$-dual satisfies any Koszul duality axioms. 
From the discussion above we see that $!$-dual does agree with Koszul duality in the case of associative algebras.\footnote{It is not difficult to see that $!$-duality for locally constant factorization algebras on $\R^n$ agrees with $\EE_n$ Koszul duality between $\clie^\bu(\fg)$, viewed as an $\EE_n$ algebra, and the $\EE_n$ enveloping algebra $U_{\EE_n} \fg$ \cite{Knudsen, Lurie,...}}

With an eye towards couplings, we do point out a universality that is satisfied by $!$-duality. 
In \cite[Chapter ??]{CG2} a factorization algebra enhancement of Noether's theorem is formulated. 
The general context is the following: 
\begin{itemize}
\item $\Obs$ is the factorization algebra of classical observables of a theory in the BV formalism on a manifold $M$.
\item $\cG$ is a local Lie algebra on $M$ which acs on the theory by local symmetries. 
\end{itemize}
Then, the classical version of Noether's theorem for factorization algebras produces a map of factorization algebras 
\[
\clie_\bu(\cG_c) \to \Obs .
\]

We arrive at $!$-duality in our situation above in the case that $\Obs$ is a factorization algebra of the form $\clie^\bu(\cL)$ where $\cL$ is another local $L_\infty$ algebra on $M$. 
This is always possible in the BV formalism: on an open set $U$ the space of Maurer--Cartan elements in the $L_\infty$ algebra $\cL(U)$ is the space of solutions to the equations of motion on $U$.
Thus, tautologically, the local Lie algebra $\cL$ is a symmetry of the classical theory.

@@

For any open set $U \subset \C^3$ we can consider the following $\C^\times$ action on the fields of the eleven-dimensional theory supported on $\R \times \C^2 \times U$ defined by
\begin{itemize}
\item On the fields $\mu(t;w,z) \in \Omega^\bu(\R) \otimes \PV^{1,\bu}(\C^2 \times U)$ the action is
\[
\lambda \cdot \mu(t;w,z) = \mu(\lambda t;\lambda w , z).
\]
\item On the fields $\nu(t;w,z) \in \Omega^\bu(\R) \otimes \PV^{0,\bu}(\C^2 \times U)$ the action is
\[
\lambda \cdot \nu(t;w,z) = \nu(\lambda t;\lambda w , z).
\]
\item On the fields $\beta(t;w,z) \in \Omega^\bu(\R) \otimes \Omega^{0,\bu}(\C^2 \times U)$ the action is
\[
\lambda \cdot \beta(t;w,z) = \lambda^{-1} \beta(\lambda t;\lambda w , z).
\]
\item On the fields $\gamma(t;w,z) \in \Omega^\bu(\R) \otimes \Omega^{1,\bu}(\C^2 \times U)$ the action is
\[
\lambda \cdot \gamma(t;w,z) = \lambda^{-1} \gamma(\lambda t;\lambda w , z).
\]
\end{itemize}

@@

\begin{prop}
For each $n$, the sheaf of cochain complexes $U \mapsto \Bar{\pi}_* \cL_{sugra}(U)^{(n)}$ is quasi-isomorphic to one of the form
\[
\Omega^{0,\bu}(U, \cV^{(n)})
\]
for some finite rank super holomorphic vector bundle $\cV^{(n)}$ on $\C^3$.
For each $n$, the differential is of the form $\dbar + Q^{hol}$.
In particular, this endows $\Bar{\pi}_* \cL_{sugra}$ with the structure of a pro-vector bundle on $\C^3$. 
\end{prop}

\parsec[s:weight-1]

As an example, let us consider the weight $(-1)$ piece of the decomposition $\Omega^{0,\bu}(Z, \cV^{(-1)})$. 
We will show that 
\[
\cV^{(-1)} = K^{-1/2}_Z \otimes \C^2 \oplus \cO_Z \oplus \Pi \T^*_Z 
\]
whose Dolbeault forms are equipped with the $\dbar$ operator and the $\del$ operator which takes functions to one-forms.

Explicitly weight zero summand $\cV^{(0)}$ consists of:
\begin{itemize}
\item 
Vector fields which are locally of the form $f^a(z) \del_{w_a}$ where $f^{a}(z)$ is a holomorphic function on $\C^3$.
Notice that these vector fields are automatically divergence-free.
Since $\del_{w_a}$ is treated as a section of $K^{-1/2}_Z$ we see that these are local sections of $K^{-1/2}_Z \otimes \C^2$. 
\item 
Next there are holomorphic functions (type $\beta$) and holomorphic $one$-forms (type $\gamma$) which do not depend on $w_a$. 
Since $\del$ is weight zero for the decomposition these forms combine to form the $\Z/2$ graded complex of sheaves
\[
\cO_Z \xto{\del} \Pi \Omega^{1,hol}_Z .
\]
\end{itemize}

\parsec[s:weight0]

Particularly important for us will be the weight zero part $\Omega^{0,\bu}(Z, \cV^{(0)})$ of the $\Z/2$ graded $L_\infty$ algebra $\Bar{\pi}_* \cL_{sugra}$ which inherits the structure of a $\Z/2$ graded $L_\infty$ algebra.
When $Z = \C^3$ we will see that the global sections of this $\Z/2$ graded $L_\infty$ algebra is quasi-isomorphic to the exceptional Lie algebra $E(3|6)$ studied by Kac \cite{KacClass}.
In other words, the weight zero piece is a local Lie algebra enhancement of this exceptional Lie algebra.

As a holomorphic vector bundle, we will see that
\[
\cV^{(0)} = \T_Z \oplus \lie{sl}(2) \otimes \cO_Z \oplus \Pi \left( \T^*_Z \otimes K^{-1/2}_Z \otimes \C^2 \right).
\]
The $L_\infty$ structure of $\cL_{sugra}$ endows the sheaf of sections of this holomorphic vector bundle with a Lie bracket which we will describe.

Explicitly, we enumerate all weight zero holomorphic sections:
\begin{itemize}
\item Vector fields which are locally of the form $\mu = f^i(z) \del_{z_i}$ or $\mu = g(z) A^{ab} w_a \del_{w_b}$ where $(A^{ab}) \in \lie{sl}(2)$.
\item Holomorphic functions of the form $\beta = w_a f(z)$ and holomorphic one-forms of the form $\gamma = g^{a}(z) \d w_a + h^{a} (z) w_a \d z$. 
Since $\del$ is weight zero, such sections are equipped with a differential 
\[
\Gamma^{hol}(Z, K^{1/2}) \xto{D} \Pi \Gamma^{hol}(Z, K^{1/2}) \oplus \Pi\Omega^{1,hol}(Z, K^{1/2}) 
\]
which sends $w_a f(z) \mapsto (f(z) , w_a \del f (z))$. 
The $\Z/2$ graded complex of sheaves is clearly equivalent to $\Pi\Omega^{1,hol}(Z, K^{1/2})$. 
\end{itemize}

\parsec[s:??]

@@

\begin{prop}
Let $Z$ be a Calabi--Yau three-fold and $\pi \colon Z \times \C^2 \times \R \to Z$ be the projection. 
There is a pro local Lie algebra $\Bar{\pi}_*\cL_{sugra}$ and a factorization algebra $\Bar{\pi}_* \Obs_{sugra} = \clie^\bu(\Bar{\pi}_* \cL_{sugra})$ on $Z$ such that:
\begin{itemize}
\item[(1)] there is a natural inclusion of of factorization algebras on $Z$
\[
\Bar{\pi}_* \Obs_{sugra} \hookrightarrow \pi_* \Obs_{sugra}
\]
which is dense at the level of cohomology. 
\item[(2)] there is a weight grading on $\cL_{\pi,sugra}$ which is concentrated in degrees $\geq -1$ and gives rise to a decomposition of vector bundles
\beqn\label{eqn:decomp3}
\Bar{\pi}_{*} \cL_{sugra} = \prod_{n \geq -1} \cV_{n} 
\eeqn
\item[(3)]
In weight zero, there is an equivalence of local Lie algebras on $Z$ 
\[
\cV_0 \simeq \cE(3|6)|Z 
\]
where $\cE(3|6)|Z$ is a local Lie algebra enhancement of the exceptional simple super Lie algebra $E(3|6)$. 
\end{itemize}
\end{prop}

@@

\parsec[s:e36]
The exceptional super Lie algebra $E(3|6)$

Let $Z$ be a complex manifold of complex dimension three equipped with a square-root of the canonical bundle.
To freely resolve the space of holomorphic sections
we employ the Dolbeault complex of the appropriate holomorphic vector bundle. 
For holomorphic vector fields we introduce the dg Lie algebra
\[
\Omega^{0,\bu}(X , \T_X)
\]
of $(0,\bu)$ Dolbeault forms with values in the holomorphic tangent bundle. 
Also, for any holomorphic vector bundle $V$ let
\[
\Omega^{-1/2 , \bu}(X, V) = \Omega^{0,\bu}(X , V \otimes \T_X^* \otimes \sigma^{-1}) .
\]

@@

We define a super dg Lie algebra to be a $\Z \times \Z/2$ graded Lie algebra $\fg = \fg_+^\bu \oplus \Pi \fg_-^\bu$ which satisfies totalized graded skew symmetry and is equipped with a differential $\d$ of bidegree $(1,+)$ that is square zero and a derivation for the bracket. 
For more details see \cite[Section 2]{EHSW}.

\begin{dfn}
Let $\sigma$ and $P$ be as above. 
Define the following local super Lie algebra $\cE_{P,\sigma}$ on $X$ whose even and odd parts are
\begin{align*}
\cE_{P,\sigma,+} & = \Omega^{0,\bu}(X , \T_X) \oplus \Omega^{0,\bu}(X , \ad P)\\
\cE_{P,\sigma,-} & = \Omega^{1 , \bu}(X, R_X \otimes \sigma^{-1}) .
\end{align*}
The differential is given by the natural $\dbar$-operator whenever it makes sense.
The bracket is defined analogously as in formulas \brian{ref}. 
\end{dfn}

On $X = \C^3$ there is a natural choice for $\sigma = K^{1/2}_{\CC^3}$, and we can take $P$ to be the trivial $SL(2)$ bundle. 
With these choices we have the following easy lemma.

%\end{document}
